\Large \bf TBD

### 2021-08-31 LaTeX-ACM/sections/paper.tex
comparison table done (down to 20 pages)

\paragraph[Centralized Exchanges (CEX)]{Centralized Exchanges (CEX)\eatpunct} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

>>>>

\paragraph[Centralized Exchanges (CEX).] Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

### 2021-08-31 LaTeX-LNCS-2022/sections/paper.tex
comparison table penciled in (needs edits)
comparison table done (down to 20 pages)

%\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode. This is not free. When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of \emph{gas}. The function caller will pledge to pay a certain amount of Ethereum's internal currency \emph{ETH} (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it. The function caller is charged for exactly what the transaction costs to execute, and they cap the maximum they are willing to be charged (\textit{gas limit}). If the cap is too low to complete the execution, the miner keeps the Gwei and \emph{reverts} the state of the EVM (as if the function never ran).
%
%A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block. As of the time of writing, the limit is approximately 11M gas. Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit. Later, we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.

\subsection{Trade Execution Systems} %NEW:@Mahsa

\emph{Order-driven} markets are a  group of trade execution systems where offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book and executed based on matching rules enforced by the market. These markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction). Table~\ref{tab:exchanges} presents three types of order-driven exchanges:

\input{tables/tradeexecutions.tex}
\begin{itemize}

\item\textbf{Centralized Exchanges (CEX).} Here, a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution.

\item\textbf{Decentralized Exchanges (DEX).} These are hybrid order-driven exchanges with some trusted off-chain components and some on-chain functionalities. DEXes were first envisioned as operating fully on-chain, but performance limitations drove developers to move key components, such as the order matching system, off-chain to a centralized database. A landscape of DEX designs exist (\eg EtherDelta, 0x, IDEX, \etc): many avoid taking custodianship of assets off-chain, and virtually all (for order-driven markets) operate the order book itself off-chain (a regulatory hook).

\item\textbf{Fully On-chain Exchanges.} Order matching can be performed `on-chain' by deploying the order-matching system either on a dedicated blockchain or inside a decentralized application (DApp). In this model, traders entrust their assets to an autonomously operating DApp with known source code instead of a third party custodian that can abscond with or lose the funds. The trading rules will operate as coded, clearing and settling can be guaranteed, and order submission is handled by the blockchain---a reasonably fair and transparent system (but see front-running; Section~\ref{sec:front}). Finally, anyone can create an on-chain order book for any asset (on the same chain) at any time. 
\end{itemize}
Despite having a superior threat model, fully on-chain order-driven exchanges are slow, difficult to regulate and implement (see Table~\ref{tab:exchanges}). In this paper, we focus on benchmarking an order book for the public blockchain Ethereum.

%\input{tables/eval.tex}

%\subsection{Trade Execution Systems}
%There are three main approaches to arranging a trade~\cite{Har03}. In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction).

@@

%%\input{tables/eval.tex}
%\paragraph{Centralized Exchanges (CEX).} Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.

>>>>

%\textbf{Ethereum's Gas Model.} Every transaction results in the participating nodes having to execute bytecode. This is not free. When a transaction is executed, each opcode in the execution path accrues a fixed, pre-specified amount of \emph{gas}. The function caller will pledge to pay a certain amount of Ethereum's internal currency \emph{ETH} (typically quoted in units of Gwei which is one billionth of an ETH) per unit of gas, and miners are free to choose to execute that transaction or ignore it. The function caller is charged for exactly what the transaction costs to execute, and they cap the maximum they are willing to be charged (\textit{gas limit}). If the cap is too low to complete the execution, the miner keeps the Gwei and \emph{reverts} the state of the EVM (as if the function never ran).
%
%A miner can include as many transactions (typically preferring transactions that bid the highest for gas) that can fit under a pre-specified \textit{block gas limit}, which is algorithmically adjusted for every block. As of the time of writing, the limit is approximately 11M gas. Essentially, our main research question is how many on-chain trades can be executed without exceeding that limit. Later, we also discuss several bytecode operations (\emph{opcodes}) that refund gas (\ie cost negative gas), which we heavily utilize in our optimizations.
\subsection{Trade Execution Systems}

There are three main approaches to arranging a trade~\cite{Har03}. In a \emph{quote-driven} market, a dealer uses its own inventory to offer a price for buying or selling an asset. In a \emph{brokered exchange}, a broker finds a buyer and seller. In an \emph{order-driven} market, offers to buy (\emph{bids}) and sell (\emph{offers}/\emph{asks}) from many traders are placed as orders in an order book. Order-driven markets can be \emph{continuous}, with buyers/sellers at any time adding orders to the order book (\emph{makers}) or executing against an existing order (\emph{takers}); or they can be \emph{called}, where all traders submit orders within a window of time and orders are matched in a batch (like an auction). Table~\ref{tab:eval2} illustrates various trade execution systems and summerizes their advantages and disadvantages.

\input{tables/eval2.tex}
%========================Following section is already covered in the table========================%

@@

%\paragraph{Centralized Exchanges (CEX)}Traditional financial markets (\eg NYSE and NASDAQ) use order-matching systems to arrange trades. An exchange will list one or more assets (stocks, bonds, derivatives, or more exotic securities) to be traded with each other, given its own order book priced in a currency (\eg USD). Exchanges for blockchain-based assets (also called crypto assets by enthusiasts) can operate the same way, using a centralized exchange (CEX) design where a firm (\eg Binance, Bitfinex, \etc) operates the platform as a trusted third party in every aspect: custodianship over assets/currency being traded, exchanging assets fairly, offering the best possible price execution. Security breaches and fraud in centralized exchanges  (\eg MtGox~\cite{TheHisto45:online}, QuadrigaCX~\cite{SEBIOrde83:online}, and many others) have become a common source of lost funds for users, while accusations of unfair trade execution have been levelled but are difficult to prove. Today, CEXes are often regulated as other money service businesses---this provides some ability for the government to conduct financial tracking but does little to provide consumer protection against fraud.
